Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-10-26 acknowledgments.tex
added missing acknowledgments and fixed a typo.

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Institute of Technology,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
Princeton University,
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Southern Methodist University,
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Colorado at Boulder,
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.

Computational resources for \enzo\ development have come from the NSF
XSEDE program, the NASA High Performance Computing program, the DOE INCITE
program, and the DOE Advanced Simulation and Computing (ASC) program.

>>>>

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Institute of Technology,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications at the University
of Illinois in Urbana-Champaign, 
the Pennsylvania State University,
the San Diego Supercomputer Center at US San Diego (through the Strategic Applications
Partner program and the Director’s office),
Princeton University,
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Southern Methodist University,
Stanford University,
the Texas Advanced Computing Center at the University of Texas,
the University of Arizona,
the University of California at San Diego, 
the University of California at Santa Cruz,
the University of Colorado at Boulder and the Janus supercomputing collaboration,
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.

Computational resources for \enzo\ development have come from the NSF
XSEDE program (at NCSA, SDSC, and TACC), the NASA High-End Computing program (through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center), the DOE INCITE
program, the DOE Advanced Simulation and Computing (ASC) program, and
the Oak Ridge Leadership Computing Facility.
